Fisheries example integrating FLR

### 2018-08-17 notebook/ms/SI5.Rmd
Attempt to addres Reviewer 1 minor comment 4 -- note multiple attempts make it clear that axis labels cannot be adjusted in FLR, so explain why this is the case

Diagnostic plots, identical to those of the [modelling stock-recruitment tutorial](http://www.flr-project.org/doc/Modelling_stock_recruitment_with_FLSR.html) for the `nsher_ri` example, are shown below.

```{r, fig.height = 6.2, fig.cap = "Output of the FLR plot function for an example Ricker model of stock recruitment on North Sea Herring data."}
plot(newFL);
```

>>>>

Diagnostic plots, identical to those of the [modelling stock-recruitment tutorial](http://www.flr-project.org/doc/Modelling_stock_recruitment_with_FLSR.html) for the `nsher_ri` example, are shown below. We note that these plots are made using the `FLCore` package, and are not produced by, nor available in, the `GMSE` package.

```{r, fig.height = 5.2, fig.cap = "Output of the FLR plot function for an example Ricker model of stock recruitment on North Sea Herring data."}
plot(newFL, cex = 0.7);
```
